An Imaging Search for Circumstellar Companions of Sirius B

### 2021-08-12 paper/paper.tex
update paper

Typical targets for imaging are nearby young stars; the close proximity means the same angular separation probes a smaller physical separation, allowing for studies closer to solar-system scales. Younger exoplanets are hotter and therefore brighter, reducing the flux ratio between the planet and its host star. Another way to reduce contrast would be to make the star fainter, which is precisely what happens in the latest stages of stellar evolution during the white dwarf cooling sequence. When intermediate mass stars (\qtyrange{1}{8}{\solarmass}) eventually exit the main-sequence (MS) they expand up to $\sim$100s of stellar radii during the red giant branch (RGB) phase. This expansion will engulf planets within the star's Roche limit. Then, during the asymptotic giant branch (AGB) phase, mass loss will adiabatically expand any orbits. Finally, once the star becomes a white dwarf it begins cooling, which reduces its luminosity by 3 to 4 orders of magnitude compared to its MS progenitor. The faintness, broad spectral lines, and expanded orbits make white dwarfs exceptionally challenging for the transit photometry and radial velocity methods. However, the reduced contrast due to the faintness of the star, and the expanded separation of planets both benefit imaging.

@@

There is limited knowledge of planetary systems around evolved stars. \citet{burleigh_imaging_2002,veras_post-main-sequence_2016} suggest exoplanets on initially wide ($>$\qty{5}{\au}) orbits around intermediate mass stars will survive expansion during the RGB phase. Close-in planets that escape the Roche limit of the expanding red giant can still be shredded by tidal forces, although the tidal forces on planets that readily escape engulfment are negligible \citep{nordhaus_orbits_2013}. During the AGB phase, stellar mass loss will adiabatically expand the orbit of the planet by a maximum factor of $M_{*,\mathrm{MS}}/M_{*,\mathrm{WD}}$ \citep{jeans_cosmogonic_1924}. In addition to \textit{first-generation} planets there are potential methods for \textit{second-generation} planets to form after the violent RGB and AGB phases \citep{perets_second_2010}.

@@

The age of the Sirius system is has much better precision than most stars ($\sim$1\% vs. $\sim$10\% or worse), which is paramount for estimating the mass of a companion from photometry. Because Sirius B is relatively young, the age uncertainty exponentially affects planet mass uncertainty due to the rapid cooling of young planets ($<$\qty{1}{\giga\year}) \citep{fortney_giant_2010}. The high system age precision is primarily derived from the well-defined dynamical masses of the binary. With well-known masses, isochrones and stellar evolution codes can be combined to pinpoint the age. The dynamical masses are determined through astrometric studies; the first study of Sirius was performed by \citet{bessel_variations_1844}, who recognized wobbles in the proper motion of Sirius A caused by a ``dark satellite''. This dark satellite was visually confirmed in \citet{bond_companion_1862} as Sirius B. \citet{adams_spectrum_1915} took the first spectral measurements of Sirius B and found it to be similar to a MS early A-type star, despite its faintness, which we now know to be typical of white dwarf spectra.

@@

\begin{deluxetable*}{ccccccccc}
    \tabletypesize{\small}
    \tablecaption{Observing parameters for the three epochs of data. All observations were carried out using the NIRC2 Lp-band filter. Observation time is based on the frames that were selected for processing. Seeing values are measured at \qty{0.5}{\micro\meter} using a differential image motion monitor (DIMM) and averaged over the observing session. Seeing values, temperature, and water vapor measurements are all provided by the Maunakea weather center forecast archive.
    \label{tbl:obs}}
    \tablehead{
        \colhead{\makecell{Date\\observed}} &
        \colhead{\makecell{Sirius B\\offset} (\unit{\arcsecond})} &
        \colhead{\makecell{Sirius B\\PA} (\unit{\degree})} &
        \colhead{\makecell{Obs.\\time} (hr)} &
        \colhead{\makecell{FOV\\rotation} (\unit{\degree})} &
        \colhead{FWHM (\unit{\milliarcsecond})} &
        \colhead{Seeing (\unit{\arcsecond})} &
        \colhead{Temp (\unit{\celsius})} &
        \colhead{PWV (\unit{\milli\meter})}
    }
    \startdata
    2020-02-04 & 11.20 & 67.90 & 1.44 & 60.1 & 79.9 & 0.936 & 0.0 & 0.7 \\
    2020-11-21 & 11.27 & 66.42 & 2.91 & 91.4 & 76.4 & 0.871 & 0.75 & 3.5 \\
    2020-11-28 & 11.27 & 66.38 & 2.44 & 80.4 & 82.2 & 1.23 & -1.5 & 3.0 \\
    \enddata
\end{deluxetable*}

@@

Despite Sirius B being the brightest white dwarf in the sky, it is still 10 magnitudes fainter than Sirius A, making it a technically challenging target, especially on ground-based telescopes. We directly imaged Sirius B with Keck/NIRC2 in Lp-band (\qty{3.776}{\micro\meter}) across three epochs in 2020 (\autoref{tbl:obs}). Our first attempt to observe Sirius B failed due to the strong scattered light from Sirius A. The adaptive optics (AO) calibration failed when the scattered light from Sirius A would sweep into the FOV of the wavefront sensor (WFS). Similarly, trying to deploy the focal-plane vortex coronagraph \citep{serabyn_w_2017} failed when the coronagraphic pointing control algorithm, QACITS \citep{huby_w_2017}, performed erratically in the presence of the scattered light. \citet[\S2]{vigan_high-contrast_2015} reported similar issues in their attempts to image Sirius B coronagraphically. In order to overcome these obstacles, we decided to try using Sirius A as the AO guide star and off-axis guiding to Sirius B.

The Keck AO system \citep{wizinowich_performance_2000} was saturated by Sirius A, so we attenuated the flux using a narrow laser-line filter to avoid saturating the WFS. While still bright (appearing like a $\sim$5 magnitude star on the WFS), this was enough attenuation to close the AO loop. From here, we slewed off-axis using the separations and position angles calculated in \autoref{tbl:obs} from the orbital parameters in \citet{bond_sirius_2017}. In this mode, we noticed higher than usual drift in the focal plane, requiring manually recentering the target every 5 or 10 minutes. We tried deploying the vortex coronagraph along with QACITS, but the diffracted light from Sirius A made QACITS unstable, so we decided to forego any coronagraphy for the remaining observations.

During each observation, we took dark frames and sky flat frames for calibration. We also disabled the field rotator, which caused the FOV to rotate throughout the night for angular differential imaging \citep[ADI;][]{marois_angular_2006}.

@@

@@

The raw images from NIRC2 required pre-processing before analyzing them for companions. For each epoch we applied a flat correction using calibration frames captured during observing. We also removed bad pixels using a combination of L.A.Cosmic \citep{van_dokkum_cosmic-ray_2001} and an adaptive sigma-clipping algorithm. We removed sky background using a high-pass median filter with a box size of 31 pixels. For both the November epochs we tried exploiting the large focal plane drifts by dithering between two positions in order to simplify background subtraction, but this ended up performing worse than the high-pass filter. At this point frames were manually selected to remove bad frames, especially those with diffraction spikes from Sirius A within a few hundred pixels, like in \autoref{fig:spike}. Then, each good frame was co-registered to sub-pixel accuracy using the algorithm presented in \citet{guizar-sicairos_efficient_2008}, followed by fitting each frame with a Gaussian PSF to reach floating-point centroid accuracy.

@@

A common problem when using subspace-driven post-processing algorithms like PCA, NMF, or GreeDS is choosing the size of the subspace (i.e., the number of components). For PCA, NMF, and GreeDS algorithms, we created residual cubes for increasing number of components, from 1 to 10. We chose 10 as the max number of components because we saw a dramatic decline in contrast sensitivity after the first few components (\autoref{fig:pca-contrast-curves}). In our analysis we employed the STIM largest intensity mask map \citep[SLIM map;][]{pairet_signal_2020} as an ensemble statistic. The SLIM map calculates the average STIM map from many residual cubes along with the average mask of the $N$ most intense pixels in each STIM map. A real companion ought to be present in many different residual cubes from the same dataset, so this ensemble approach can give us a probability map without predetermining the number of components. The collapsed residual frames, average STIM map, SLIM map, and contrast curves for each epoch for each of the above algorithms are in \autoref{sec:adi-results}.

All of the ADI algorithms and metrics are implemented in the open-source Julia package ADI.jl \citep{lucas_adijl_2020}. All of the code for the ADI processing in this paper, including the scripts for each figure produced are in a GitHub repository in Jupyter notebooks and Julia scripts (\href{https://github.com/mileslucas/sirius-b}{https://github.com/mileslucas/sirius-b}).

@@

\begin{figure*}[t]
    \centering
    \epsscale{1}
    \plotone{contrast_curves}
    \caption{The contrast curves for the best performing algorithm from each epoch. The solid lines are the Gaussian 5$\sigma$ contrast curves and the dashed lines are the Student-t corrected curves. The mean uncertainty from the total system age ($\sim$\qty{10}{\mega\year}) is shown by a lone error bar. In addition, the expected upper limit for orbital separation of a stable orbit of \qty{1.5}{\au} is plotted as a vertical dashed line. The companion mass values are interpolated from the AMES-Cond grid. The lower mass limit (upper magnitude limit) of these models is plotted in a light-gray horizontal dashed line. The annular PCA curve is cut off because the contrast in the innermost annulus was greater than 1.}
    \label{fig:contrast}
\end{figure*}

@@

The reduced images do not show consistent or significant evidence for a substellar companion. The STIM probability maps for the 2020-11-21 and 2020-11-28 epochs suggest evidence for some blobs $\sim$\ang{;;0.13} ($\sim$1.6 FWHM) from the center. The lack of evidence in the February epoch and the significance maps as well as the proximity to the central star both reduce the probability of these blobs being true companions. Nonetheless, we estimated astrometry for blobs from each epoch (\autoref{tbl:astrometry}) and tried fitting Keplerian orbits using the ``Orbits for the Impatient'' algorithm \citep[OFTI;][]{blunt_orbits_2017}. We generated $10^4$ orbits, none of which managed to contain the points from each epoch (\autoref{sec:orbits}). We take this as direct evidence against the blobs being substellar companions of any kind.

It is interesting to note the morphology of the innermost $\sim$\ang{;;0.4} in the frames produced by GreeDS and NMF. Both of these algorithms usually outperform traditional median and PCA subtraction for disk imaging. In the frames from each epoch, but particularly in the two November epochs, a symmetric ``barbell'' shape can be seen which is similar to other disk images \citep[e.g., fig.~7][]{norris_vampires_2014}. Due to the nature of high-contrast imaging, it is difficult to differentiate systematic noise from real signal in the speckle-limited regime, in addition there is no prior evidence for a circumstellar disk from IR excess. Follow-up work in the visible (e.g., Subaru/VAMPIRES, VLT/SPHERE) may be able to image such a disk.

@@

@@

\begin{deluxetable}{ccc}[h!]
    \tablecaption{Provisional astrometry for blobs of interest from each epoch. The separation and offset are in relation to Sirius B. The uncertainties are derived from the FWHM of the PSF from each epoch.
    \label{tbl:astrometry}}
    \tablehead{
        \colhead{Date observed} &
        \colhead{offset (\unit{\milliarcsecond})} &
        \colhead{PA (\unit{\degree})}
    }
    \startdata
    2020-02-04 & $114\pm 40$ & $-115\pm 20$  \\
    2020-11-21 & $121\pm 38$ & $-119\pm 18$  \\
    2020-11-28 & $114\pm 41$ & $-113\pm 21$  \\
    \enddata
\end{deluxetable}

\begin{figure}[h!]
    \centering
    \figurenum{13}
    \plotone{orbit_frames}
    \caption{Provisional astrometry (white circles) displayed on STIM maps using the GreeDS algorithm with 2 components. Each frame was cropped to the inner \ang{;;0.25} and the inner FWHM has been masked out. The width of the circles represent the uncertainty.}
    \label{fig:prov-orbit}
\end{figure}

>>>>

Typical targets for imaging are nearby young stars; the close proximity means the same angular separation probes a smaller physical separation, allowing for studies closer to solar-system scales. Younger exoplanets are hotter and therefore brighter, reducing the flux ratio between the planet and its host star. Another way to reduce contrast would be to image a faint star with bright companions, such as a young white dwarf (WD) star. When intermediate mass stars (\qtyrange{1}{8}{\solarmass}) eventually exit the main-sequence (MS) they expand up to $\sim$100s of stellar radii during the red giant branch (RGB) phase. This expansion will engulf planets within the star's Roche limit. Then, during the asymptotic giant branch (AGB) phase, mass loss will adiabatically expand any orbits. Finally, once the star becomes a white dwarf it begins cooling, which reduces its luminosity by 3 to 4 orders of magnitude compared to its MS progenitor. The faintness, broad spectral lines, and expanded orbits make white dwarfs exceptionally challenging for the transit photometry and radial velocity methods. However, the reduced contrast due to the faintness of the star, and the expanded separation of planets both benefit imaging.

@@

There is limited knowledge of planetary systems around evolved stars. \citet{burleigh_imaging_2002,veras_post-main-sequence_2016} suggest exoplanets on initially wide ($>$\qty{5}{\au}) orbits around intermediate mass stars will survive expansion during the RGB phase. Close-in planets that escape the Roche limit of the expanding red giant can still be shredded by tidal forces, although the tidal forces on planets that readily escape engulfment are negligible \citep{nordhaus_orbits_2013}. During the AGB phase, stellar mass loss will adiabatically expand the orbit of the planet by a maximum factor of $M_{*,\mathrm{MS}}/M_{*,\mathrm{WD}}$ \citep{jeans_cosmogonic_1924}. In addition to \textit{first-generation} planets, there are potential methods for \textit{second-generation} planets to form after the violent RGB and AGB phases \citep{perets_second_2010}.

@@

The age of the Sirius system has much better precision than most stars ($\sim$1\% vs. $\sim$10\% or worse), which is paramount for estimating the mass of a companion from photometry. Because Sirius B is relatively young, the age uncertainty exponentially affects planet mass uncertainty due to the rapid cooling of young planets ($<$\qty{1}{\giga\year}) \citep{fortney_giant_2010}. The high system age precision is primarily derived from the well-defined dynamical masses of the binary. With well-known masses, isochrones and stellar evolution codes can be combined to pinpoint the age. The dynamical masses are determined through astrometric studies; the first study of Sirius was performed by \citet{bessel_variations_1844}, who recognized wobbles in the proper motion of Sirius A caused by a ``dark satellite''. This dark satellite was visually confirmed in \citet{bond_companion_1862} as Sirius B. \citet{adams_spectrum_1915} took the first spectral measurements of Sirius B and found it to be similar to a MS early A-type star, despite its faintness, which we now know to be typical of white dwarf spectra.

@@

\begin{deluxetable*}{ccccccccc}
    \tabletypesize{\small}
    \tablecaption{Observing parameters for the three epochs of data. All observations were carried out using the NIRC2 Lp-band filter. Observation time is based on the frames that were selected for processing. Seeing values are measured at \qty{0.5}{\micro\meter} using a differential image motion monitor (DIMM) and averaged over the observing session. Seeing values, temperature, and water vapor measurements are all provided by the Maunakea weather center forecast archive.
    \label{tbl:obs}}
    \tablehead{
        \colhead{\makecell{Date\\observed}} &
        \colhead{\makecell{Sirius B\\offset} (\unit{\arcsecond})} &
        \colhead{\makecell{Sirius B\\PA} (\unit{\degree})} &
        \colhead{\makecell{Obs.\\time} (hr)} &
        \colhead{\makecell{FOV\\rotation} (\unit{\degree})} &
        \colhead{FWHM (\unit{\milliarcsecond})} &
        \colhead{Seeing (\unit{\arcsecond})} &
        \colhead{Temp (\unit{\celsius})} &
        \colhead{PWV (\unit{\milli\meter})}
    }
    \startdata
    2020-02-04 & 11.20 & 67.90 & 1.44 & 60.1 & 79.9 & 0.936 & 0.0 & 0.7 \\
    2020-11-21 & 11.27 & 66.42 & 2.91 & 91.4 & 76.4 & 0.871 & 0.8 & 3.5 \\
    2020-11-28 & 11.27 & 66.38 & 2.44 & 80.4 & 82.2 & 1.23 & -1.5 & 3.0 \\
    \enddata
\end{deluxetable*}

@@

Despite Sirius B being the brightest white dwarf in the sky, it is still 10 magnitudes fainter than Sirius A, making it a technically challenging target, especially on ground-based telescopes. We directly imaged Sirius B with Keck/NIRC2 in Lp-band (\qty{3.776}{\micro\meter}) using the narrow camera (\qty{10}{\milliarcsecond\per px}; \ang{;;2.5}$\times$\ang{;;2.5}) across three epochs in 2020 (\autoref{tbl:obs}). Our first attempt to observe Sirius B failed due to the strong scattered light from Sirius A. The adaptive optics (AO) calibration failed when the scattered light from Sirius A would sweep into the FOV of the wavefront sensor (WFS). Similarly, trying to deploy the focal-plane vortex coronagraph \citep{serabyn_w_2017} failed when the coronagraphic pointing control algorithm, \texttt{QACITS} \citep{huby_w_2017}, performed erratically in the presence of the scattered light. \citet[\S2]{vigan_high-contrast_2015} reported similar issues in their attempts to image Sirius B coronagraphically. In order to overcome these obstacles, we decided to try using Sirius A as the AO guide star and off-axis guiding to Sirius B.

The Keck AO system \citep{wizinowich_performance_2000} was saturated by Sirius A, so we attenuated the flux using a narrow laser-line filter to avoid saturating the WFS. While still bright (appearing like a $\sim$5 magnitude star on the WFS), this was enough attenuation to close the AO loop. From here, we slewed off-axis using the separations and position angles calculated in \autoref{tbl:obs} from the orbital parameters in \citet{bond_sirius_2017}. In this mode, we noticed higher than usual drift in the focal plane, requiring manually recentering the target every 5 or 10 minutes. We tried deploying the vortex coronagraph along with \texttt{QACITS}, but the diffracted light from Sirius A made \texttt{QACITS} unstable, so we decided to forego any coronagraphy for the remaining observations.

During each observation, we took dark frames and sky flat frames for calibration. All observations were taken with the telescope's field rotator set to track the telescope pupil in order to exploit the natural rotation of the sky via angular differential imaging \citep[ADI;][]{marois_angular_2006}.

@@

\begin{figure*}
    \centering
    \epsscale{1}
    \plotone{contrast_curves}
    \caption{The contrast curves for the best performing algorithm from each epoch. The solid lines are the Gaussian 5$\sigma$ contrast curves and the dashed lines are the Student-t corrected curves. The mean uncertainty from the total system age ($\sim$\qty{10}{\mega\year}) is shown by a lone error bar. In addition, the expected upper limit for orbital separation of a stable orbit of \qty{1.5}{\au} is plotted as a vertical dashed line. The companion mass values are interpolated from the AMES-Cond grid. The lower mass limit (upper magnitude limit) of these models is plotted in a light-gray horizontal dashed line. The annular PCA curve is cut off because the contrast in the innermost annulus was greater than 1.}
    \label{fig:contrast}
\end{figure*}

@@

The raw images from NIRC2 required pre-processing before analyzing them for companions. For each epoch we applied a flat correction using calibration frames captured during observing. We also removed bad pixels using a combination of \texttt{L.A.Cosmic} \citep{van_dokkum_cosmic-ray_2001} and an adaptive sigma-clipping algorithm. We removed sky background using a high-pass median filter with a box size of 31 pixels. For both the November epochs we tried exploiting the large focal plane drifts by dithering between two positions in order to simplify background subtraction, but this ended up performing worse than the high-pass filter. At this point frames were manually selected to remove bad frames, especially those with diffraction spikes from Sirius A within a few hundred pixels, like in \autoref{fig:spike}. Then, each good frame was co-registered to sub-pixel accuracy using the algorithm presented in \citet{guizar-sicairos_efficient_2008}, followed by fitting each frame with a Gaussian PSF to reach floating-point centroid accuracy.

@@

A common problem when using subspace-driven post-processing algorithms like PCA, NMF, or GreeDS is choosing the size of the subspace (i.e., the number of components). For PCA, NMF, and GreeDS algorithms, we created residual cubes for increasing number of components, from 1 to 10. We chose 10 for the max number of components because we saw a dramatic decline in contrast sensitivity after the first few components (\autoref{fig:pca-contrast-curves}). In our analysis we employed the STIM largest intensity mask map \citep[SLIM map;][]{pairet_signal_2020} as an ensemble statistic. The SLIM map calculates the average STIM map from many residual cubes along with the average mask of the $N$ most intense pixels in each STIM map. A real companion ought to be present in many different residual cubes from the same dataset, so this ensemble approach can give us a probability map without predetermining the number of components. The collapsed residual frames, average STIM map, SLIM map, and contrast curves for each epoch for each of the above algorithms are in \autoref{sec:adi-results}.

All of the ADI algorithms and metrics are implemented in the open-source Julia package \texttt{ADI.jl} \citep{lucas_adijl_2020}. All of the code for the ADI processing in this paper, including the scripts for each figure produced are in a GitHub repository in Jupyter notebooks and Julia scripts (\href{https://github.com/mileslucas/sirius-b}{https://github.com/mileslucas/sirius-b}).

@@

@@

The reduced images do not show consistent or significant evidence for a substellar companion. The STIM probability maps for the 2020-11-21 and 2020-11-28 epochs suggest evidence for some blobs $\sim$\qty{0.3}{\au} (\ang{;;0.13}; 1.6 FWHM) from the center. The February epoch also shows a blob at a similar separation in the reduced image which does not appear in the STIM map. The lack of statistical evidence in the February epoch and the significance maps as well as the proximity to the central star both reduce the probability of these blobs being true companions. Nonetheless, we estimated astrometry for blobs from each epoch (\autoref{tbl:astrometry}) and tried fitting Keplerian orbits using the ``Orbits for the Impatient'' algorithm \citep[OFTI;][]{blunt_orbits_2017}. We generated $10^4$ orbits, none of which managed to contain the points from each epoch (\autoref{sec:orbits}). We take this as direct evidence against the blobs being substellar companions of any kind.

It is interesting to note the morphology of the innermost $\sim$\ang{;;0.4} in the frames produced by GreeDS and NMF. Both of these algorithms usually outperform traditional median and PCA subtraction for disk imaging. In the frames from each epoch, but particularly in the two November epochs, a symmetric ``barbell'' shape can be seen which is similar to other disk images \citep[e.g., fig.~7][]{norris_vampires_2014}. Due to the nature of high-contrast imaging, it is difficult to differentiate systematic noise from real signal in the speckle-limited regime, in addition there is no prior evidence for a circumstellar disk from IR excess. Follow-up work in the visible (e.g., Subaru/VAMPIRES, VLT/ZIMPOL) may be able to image such a disk.

@@

For future work, we consider two potential improvements on our observations. As mentioned in \autoref{sec:results}, optical observations using an instrument like Subaru/VAMPIRES \citep{norris_vampires_2014} or VLT/ZIMPOL \citep{schmid_zimpol_2018}. Optical observations can look for disks in the Rayleigh-scattering regime, which is not readily probed by IR observations. Furthermore, the polarimetric differential observation modes of both instruments allow for nearly diffraction-limited imaging, down to 10s of milliarcseconds. The other avenue for followup is space-based imaging, which is not to improve on the coronagraphic performance, which is still limited by the scattered light of Sirius A, but rather due to the increased zero-point sensitivity of the instruments. For example, using JWST/NIRCAM in long wavelength imaging mode has a limiting magnitude of $sim$25 in the F480M filter, which would easily reach the model mass sensitivity limits at $>$\ang{;;0.3} without saturation \citep{pontoppidan_pandeia_2016}. However, our ground-based observations are already quite close to the model limits, raising the concern of diminishing returns. Planetary atmosphere models must improve, first, before fully reaping the benefits of the additional sensitivity of space-based observations.

@@

\begin{deluxetable}{ccc}[h!]
    \tablecaption{Provisional astrometry for blobs of interest from each epoch. The separation and offset are in relation to Sirius B. The uncertainties are derived from the FWHM of the PSF from each epoch.
    \label{tbl:astrometry}}
    \tablehead{
        \colhead{Date observed} &
        \colhead{offset (\unit{\milliarcsecond})} &
        \colhead{PA (\unit{\degree})}
    }
    \startdata
    2020-02-04 & $123\pm 40$ & $-128\pm 20$  \\
    2020-11-21 & $119\pm 38$ & $68\pm 18$  \\
    2020-11-28 & $132\pm 41$ & $37\pm 21$  \\
    \enddata
\end{deluxetable}

\begin{figure}[h!]
    \centering
    \figurenum{13}
    \plotone{orbit_frames}
    \caption{Provisional astrometry (white circles) displayed on collapsed and derotated residuals from each epoch. Each frame was cropped to the inner $\sim$\qty{7}{\au} (\ang{;;0.25}) and the inner FWHM has been masked out. The width of the circles represent the uncertainty.}
    \label{fig:prov-orbit}
\end{figure}
